Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-26 table_fpp.tex
numbers changed

201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet \\

@@

201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Planet \\

@@

 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{a}\\

@@

201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Planet \\

@@

\enddata
\tablecomments{Results of the \texttt{vespa} astrophysical 
false positive probability calculations for all candidates.  
Likely false positives (FPP $> 0.9$) are marked in red.  
Candidates are declared to be validated if FPP $< 0.01$.  
EB, BEB, and HEB refer to the three considered astrophysical 
false positive scenarios, and the relative probability of 
each is listed in the appropriate column.}
\tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
\tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
\tablenotetext{a}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
\end{deluxetable*}

>>>>

201295312.01 & $0.04$ &  Y & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.21$ & $< 10^{-4}$ & Planet\tablenotemark{c} \\

@@

201546283.01 & $0.15$ &  - & $< 10^{-4}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.06$ & $1.1\times10^{-4}$ & Candidate\tablenotemark{a} \\

@@

 \color{red} 201555883.01  & \color{red}  $0.94$  & \color{red}   -  & \color{red}  $< 10^{-4}$  & \color{red}  $< 10^{-4}$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  $0.10$  & \color{red}  $3.6\times10^{-3}$  & \color{red}  FP\tablenotemark{b}\\

@@

201828749.01 & $0.39$ &  Y & $2.6\times10^{-3}$ & $< 10^{-4}$ & $< 10^{-4}$ & $0.17$ & $2.6\times10^{-3}$ & Candidate\tablenotemark{a} \\

@@

\enddata
\tablecomments{Results of the \texttt{vespa} astrophysical 
false positive probability calculations for all candidates.  
Likely false positives (FPP $> 0.9$, or otherwise designated)
 are marked in red.  
Candidates are declared to be validated planets if FPP $< 0.01$.  
EB, BEB, and HEB refer to the three considered astrophysical 
false positive scenarios, and the relative probability of 
each is listed in the appropriate column.}
\tablenotetext{1}{Maximum depth of potential secondary eclipse signal.}
\tablenotetext{2}{Whether adaptive optics observation is presented in this paper.}
\tablenotetext{3}{Integrated planet occurrence rate assumed between 0.7$\times$ and 1.3$\times$ the candidate radius}
\tablenotetext{a}{Despite low FPP, returned to candidate status 
out of abundance of caution due
to secondary star detection in or near photometric aperture.  Most of these we do anticipate to be validated once the specific false positive scenarios are considered.}
\tablenotetext{b}{Declared a false positive because of epoch match to 201569483.01 (see \S\ref{sec:ephemmatch}).}
\tablenotetext{c}{Identified as planet by \citet{Crossfield15}.}
\end{deluxetable*}
